Supplementary Information

### 2020-08-19 doc/manuscript/MEE_manuscript.Rmd
update manuscript

@@

- temperature sensitivity shifts from neg in warm climates to positive in cold climates, although @sniderhan_growth_2016 shows that the effect shifted to negative as warming progressed

- additive effects are common and should not be overlooked

- nonlinear effects occur sometimes

>>>>

 (*See [ISSUE #42 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/42)*)

@@

* temperature sensitivity shifts from neg in warm climates to positive in cold climates, although @sniderhan_growth_2016 shows that the effect shifted to negative as warming progressed

* additive effects are common and should not be overlooked

* nonlinear effects occur sometimes
